Kindly Bent to Free Us

### 2019-11-21 kindly/lang.tex
3.3.3 Copying \& Splitting: replaced @a@ with $a$.

\begin{figure}[!tb]
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
  \vspace{-10pt}
\end{figure}

@@

\begin{figure}[tp]
  \input{infer/lattice}
  \vspace{-5pt}
  \caption{Lattice ordering -- $k \lk_\Lat k'$}
  \label{sdtyp:lattice}
  \vspace{-10pt}
\end{figure}

\begin{figure*}[tp]
  % \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDRegion
      \and
      \ruleSDVar
      \and
      \ruleSDPair
      \and
      \ruleSDMatchPair
    \end{mathpar}
    \vspace{-10pt}
    \caption{Selected typing rules -- $\inferS{C}{\E}{e}{\tau}$}
    \label{selectrules:borrow}
    \label{selectrules:binders}
    \label{sdtyp:pair}
    \label{selectrules:region}
    \label{selectrules:matching}
    \vspace{-5pt}
  % \end{minipage}
\end{figure*}

@@

\begin{figure}[tp]
  \begin{align*}
    \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
    B &::=\ \bnone % \tag{Empty} \\
    \mid \bvar{\tvar}{\kschm} % \tag{Types}
    \mid \bvar{x}{\schm}% \tag{Variables}
    \mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}% \tag{Borrows}\\
    \mid \svar{x}{\schm}^n % \tag{Suspended}
    % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
  \end{align*}
  \vspace{-10pt}
  \caption{Type environments}
  \label{grammar:env}
  \vspace{5pt}
  % \begin{minipage}{0.5\linewidth}
  \centering
    \input{sdtyping/split-binder}
    \vspace{-5pt}
    \caption{Splitting rules for bindings -- $\lsplit{C}{B}{B_l}{B_r}$}
    \label{sdtyp:split}
  \vspace{-10pt}
  % \end{minipage}
\end{figure}

@@

\subsubsection{Regions}
\label{sdtyping:regions}

\begin{figure}[tp]
  % \begin{minipage}{0.4\linewidth}
  %   \centering
  %   \begin{mathpar}
  %     \ruleSDRegion
  %   \end{mathpar}
  %   \caption{The {\sc Region} rule}
  %   \label{selectrules:region}
  % \end{minipage}\hfill
  % \begin{minipage}{\linewidth}
    \centering
    % \begin{tabular}
    %   {@{}>{$}r<{$}@{ $\vdash_e$ }
    %   >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
    %   >{$}l<{$}
    %   r}

@@

    %   (\kaff_n\lk k\lk\kaff_\infty)
    %   &\svar[\MBORROW]{x}{\tau}^n
    %   &\bvar{\borrow[\MBORROW]{x}}{\borrowty[\MBORROW] k{\tau}}
    %   &Mut
    % \end{tabular}
    \begin{mathpar}
      \inferrule{
        \entail{C}{(\BORROW_n\lk k) \wedge (k \lk \BORROW_\infty)}\\
        \BORROW\in\left\{\kun,\kaff\right\}
      }{
        \lregion{C}{}
        {\svar[\BORROW]{x}{\tau}^n}
        {\bvar{\borrow[\BORROW]{x}}{\borrowty[\BORROW] k{\tau}}}
      }
    \end{mathpar}
    \vspace{-10pt}
    \caption{Borrowing rules for bindings -- $\lregion{C}{x}{\E}{\E'}$}
    \label{env:rule:borrow}
  \vspace{-10pt}
  % \end{minipage}
\end{figure}

@@

Our system would be incomplete without a way to actually manipulate resources.
We consider the simple case of an abstract resource
type $\tapp{\tres}{\tau}$ whose content of type $\tau$ must be $\kun_0$ and
equipped with four operations:
\begin{itemize}
\item
$\create$:
$\forall{\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
{\tvar \tarr{} \tapp\tres\tvar}$\\
Creates a new resource.

\item
$\observe$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
{\borrowty[\IBORROW]{\kvar}{\tapp\tres\tvar} \tarr{} \tvar}$\\
Reads from a shared borrow of a resource.

\item
$\update$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
\borrowty[\MBORROW]{\kvar}{\tapp\tres\tvar} \tarr{} \tvar \tarr{\kaff} \tunit$\\
Writes to an exclusive borrow of a resource.

\item
$\destroy$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
\tapp\tres\tvar \tarr{} \tunit$\\
Destroys a resource.
\end{itemize}

>>>>

\begin{figure}[!tb]
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure}

@@

\begin{figure}[tp]
  \input{infer/lattice}
  \caption{Lattice ordering -- $k \lk_\Lat k'$}
  \label{sdtyp:lattice}
\end{figure}

\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
  \end{minipage}\hfill

  % \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDRegion
      \and
      \ruleSDVar
      \and
      \ruleSDPair
      \and
      \ruleSDMatchPair
    \end{mathpar}
    \caption{Selected typing rules -- $\inferS{C}{\E}{e}{\tau}$}
    \label{selectrules:borrow}
    \label{selectrules:binders}
    \label{sdtyp:pair}
    \label{selectrules:region}
    \label{selectrules:matching}
  % \end{minipage}
\end{figure*}

@@

\begin{figure}[tp]
  \begin{align*}
    \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
    B &::=\ \bnone % \tag{Empty} \\
    \mid \bvar{\tvar}{\kschm} % \tag{Types}
    \mid \bvar{x}{\schm}% \tag{Variables}
    \mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}% \tag{Borrows}\\
    \mid \svar{x}{\schm}^n % \tag{Suspended}
    % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
  \end{align*}
  \vspace{-10pt}
  \caption{Type environments}
  \vspace{10pt}
  \label{grammar:env}
  % \begin{minipage}{0.5\linewidth}
  \centering
    \input{sdtyping/split-binder}
    \caption{Splitting rules for bindings -- $\lsplit{C}{B}{B_l}{B_r}$}
    \label{sdtyp:split}
  % \end{minipage}
\end{figure}

@@

\subsubsection{Regions}
\label{sdtyping:regions}
\begin{figure}[tp]
  % \begin{minipage}{0.4\linewidth}
  %   \centering
  %   \begin{mathpar}
  %     \ruleSDRegion
  %   \end{mathpar}
  %   \caption{The {\sc Region} rule}
  %   \label{selectrules:region}
  % \end{minipage}\hfill
  \begin{minipage}{\linewidth}
    \centering
    % \begin{tabular}
    %   {@{}>{$}r<{$}@{ $\vdash_e$ }
    %   >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
    %   >{$}l<{$}
    %   r}

@@

    %   (\kaff_n\lk k\lk\kaff_\infty)
    %   &\svar[\MBORROW]{x}{\tau}^n
    %   &\bvar{\borrow[\MBORROW]{x}}{\borrowty[\MBORROW] k{\tau}}
    %   &Mut
    % \end{tabular}
    \begin{mathpar}
      \inferrule{
        \entail{C}{(\BORROW_n\lk k) \wedge (k \lk \BORROW_\infty)}\\
        \BORROW\in\left\{\kun,\kaff\right\}
      }{
        \lregion{C}{}
        {\svar[\BORROW]{x}{\tau}^n}
        {\bvar{\borrow[\BORROW]{x}}{\borrowty[\BORROW] k{\tau}}}
      }
    \end{mathpar}
    \caption{Borrowing rules for bindings -- $\lregion{C}{x}{\E}{\E'}$}
    \label{env:rule:borrow}
  \end{minipage}
\end{figure}

@@

Our system would be incomplete without a way to actually manipulate resources.
We consider the simple case of an abstract resource
type $\tapp{\tres}{\tau}$ whose content of type $\tau$ must be $\kun_0$ and
equipped with four operations:
\begin{itemize}
\item
$\create$:
$\forall{\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq \kvar {\kun_0}}
{\tvar \tarr{} \tapp\tres\tvar}$\\
Creates a new resource.

\item
$\observe$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
{\borrowty[\IBORROW]{\kvar}{\tapp\tres\tvar} \tarr{} \tvar}$\\
Reads of a shared borrow of a resource.

\item
$\update$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
\borrowty[\MBORROW]{\kvar}{\tapp\tres\tvar} \tarr{} \tvar \tarr{\kaff} \tunit$\\
Writes in an exclusive borrow of a resource.

\item
$\destroy$:
$\forall{\kvar\kvar_\tvar}\bvar{\tvar}{\kvar_\tvar}.\
\qual{\Cleq {\kvar_\tvar} {\kun_0}}
\tapp\tres\tvar \tarr{} \tunit$\\
Disposes of a resource.
\end{itemize}
